A demonstration of the \LaTeXe\ class file for \itshape{SAGE Publications}

### 2015-12-09 body/intro.tex

By tackling these issues, our method proposes contributions to both problems \Pa and \Pb.
For each problem, we introduce an original formulation of the related theoretical issues.
Then, we propose a concrete implementation of the solution, where the constraints of the problem are relaxed in favor of efficiency.
The relaxation is justified empirically, with statistics presented for each robot and scenario presented\adnote{several robots and scenario, or even better, for N robots and M scenarios}. The complete framework is implemented within
the open source platform Hpp.

@@

The present paper is an extension of a conference paper to appear in the proceedings of the ISRR'15 conference~\citep(tonneauisrr15).
The conference paper focuses on the theoretical formulation of the problem, and presents results obtained with virtual avatars.
This extension completes this work with a \adnote{I remove the word 'argumented' because it does not exist and I've not been able to find a good replacement} discussion on the implementation of this theory to real-world robots and problems.
In particular, we introduce a robust balance criterion, designed to ensure the equilibrium of the robot despite bounded error in the contact forces. We also provide details on the hpp implementation
of our contact generation algorithm. Furthermore, our experiments are now applied to real-robot models, namely HRP-2 and HyQ\adnote{cite Semini}. TODO Appendix describes the generation process
for the robot.

>>>>

By tackling these issues, our method proposes contributions to both problems \Pa and \Pb.
For each problem, we introduce an original formulation of the related theoretical issues.
Then, we propose a concrete implementation of the solution, where the constraints of the problem are relaxed in favor of efficiency.
The relaxation is justified empirically, with statistics presented for each robot and scenario presented\adnote{several robots and scenario, or even better, for N robots and M scenarios}. The complete framework is implemented within
the open source platform HPP.

@@

The present paper is an extension of a conference paper to appear in the proceedings of the ISRR'15 conference~\citep(tonneauisrr15).
The conference paper focuses on the theoretical formulation of the problem, and presents results obtained with virtual avatars.
This extension completes this work with a \adnote{I remove the word 'argumented' because it does not exist and I've not been able to find a good replacement} discussion on the implementation of this theory to real-world robots and problems.
In particular, we introduce a robust balance criterion, designed to ensure the equilibrium of the robot despite bounded error in the contact forces. We also provide details on the HPP implementation
of our contact generation algorithm. Furthermore, our experiments are now applied to real-robot models, namely HRP-2 and HyQ\adnote{cite Semini}. TODO Appendix describes the generation process
for the robot.
